\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-13 methodology.tex
updates to section 4

  // cold state: repaired
  [OnEvent(NotifyEnFailure, ProcessExtentNodeFailure)]
  cold state Repaired : MonitorState {
    void ProcessExtentNodeFailure() {
        var node = GetExtentNode(this.Payload);
        ExtentNode2Replica.Remove(node);
        goto Repairing;
    }
  }

  // hot state: repairing
  [OnEvent(NotifyExtentRepaired, ProcessExtentRepaired)]
  hot state Repairing : MonitorState {
    void ProcessExtentRepaired() {
      var node = GetExtentNode(this.Payload);
      ExtentNode2Replica[node] = true;
      if (ReplicaCount == Harness.REPLICA_COUNT_TARGET)
        goto Repaired;
    }
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{The RepairMonitor machine.}
\label{fig:monitor}
%\vspace{-2mm}
\end{figure}

>>>>

  // cold state: repaired
  [OnEvent(NotifyEnFailure, ProcessExtentNodeFailure)]
  cold state Repaired {
    void ProcessExtentNodeFailure() {
        var node = GetExtentNode(this.Payload);
        ExtentNode2Replica.Remove(node);
        goto Repairing;
    }
  }

  // hot state: repairing
  [OnEvent(NotifyExtentRepaired, ProcessExtentRepaired)]
  hot state Repairing {
    void ProcessExtentRepaired() {
      var node = GetExtentNode(this.Payload);
      ExtentNode2Replica[node] = true;
      if (ReplicaCount == Harness.REPLICA_COUNT_TARGET)
        goto Repaired;
    }
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{The RepairMonitor machine.}
\label{fig:monitor}
%\vspace{-2mm}
\end{figure}
